---
title: "My First R presentation"
author: "Elisa Battistoni"
output: 
  ioslides_presentation: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## New Slide 1
Display content 1

## New Slide 2

Plain text

*italics*

**bold**

`for (i %in% 1:10)` 

## New Slide 3

***
A slide without a title


## A slide with a title
### A top level subheading
#### A second level subheading

1. item 1
2. item 2


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## My new slide with comment signs
```{r, echo = TRUE}
data("mtcars")
head(mtcars)
```


## My new slide without comment signs
```{r, echo = TRUE, comment = ""}
head(mtcars)
```


## My first slide with plot
```{r, fig.align='center', fig.cap='AWESOME!!'}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```